\section{Typeset Text}

Prepare your submissions on a word processor or typesetter.  Please
                                note that page layout may change slightly depending upon the printer
                                you have specified.  \LaTeX\ sometimes will create overfull lines
                                that extend into columns.  To attempt to combat this, the .cls
                                file has a command, {\textbackslash}sloppy, that essentially asks
                                \LaTeX\ to prefer underfull lines with extra whitespace.  For more
                                details on this, and info on how to control it more finely, check out
                                {\url{http://www.economics.utoronto.ca/osborne/latex/PMAKEUP.HTM}}.

\subsection{Title and Authors}

Your paper's title, authors and affiliations should run across the
                                full width of the page in a single column 17.8 cm (7 in.) wide.  The
                                title should be in Helvetica 18-point bold; use Arial if Helvetica is
                                not available.  Authors' names should be in Times Roman 12-point bold,
                                and affiliations in Times Roman 12-point.  For more than three authors,
                                you may have to place some address information in a footnote, or in a named
                                section at the end of your paper. Please use full international addresses and
                                telephone dialing prefixes.  Leave one 10-pt line of white space below the last
                                line of affiliations.

\subsection{Abstract and Keywords}

Every submission should begin with an abstract of about 150 words,
                                followed by a set of keywords. The abstract and keywords should be
                                placed in the left column of the first page under the left half of the
                                title. The abstract should be a concise statement of the problem,
                                approach and conclusions of the work described.  It should clearly
                                state the paper's contribution to the field of HCI.

The first set of keywords will be used to index the paper in the
                                proceedings. The second set are used to catalogue the paper in the ACM
                                Digital Library. The latter are entries from the ACM Classification
                                System~\cite{acm_categories}.  In general, it should only be necessary
                                to pick one or more of the H5 subcategories, see
                                \url{http://www.acm.org/class/1998/ccs98.html}

\subsection{Normal or Body Text}

Please use a 10-point Times Roman font or, if this is unavailable,
                                another proportional font with serifs, as close as possible in
                                appearance to Times Roman 10-point. The Press 10-point font available
                                to users of Script is a good substitute for Times Roman. If Times
                                Roman is not available, try the font named Computer Modern Roman. On a
                                Macintosh, use the font named Times and not Times New Roman. Please
                                use sans-serif or non-proportional fonts only for special purposes,
                                such as headings or source code text.

\subsection{First Page Copyright Notice}

Leave 3 cm (1.25 in.) of blank space for the copyright notice at the
                                bottom of the left column of the first page. In this template a
                                floating text box will automatically generate the required space. Note
                                however that the text box is anchored to the \textbf{ABSTRACT}
                                heading, so if that heading is deleted the text box will disappear as
                                well.  You can replace the default copyright notice by uncommenting
                                the {\textbackslash}toappear block at the beginning of the document
                                and inserting your own text, for example, for versions under review.

\subsection{Subsequent Pages}

On pages beyond the first, start at the top of the page and continue
                                in double-column format.  The two columns on the last page should be
                                of equal length.